\documentclass[twocolumn,twoside]{IEEEtran}

\usepackage{graphicx}
\usepackage{svg}

\input{include/prelude.tex}
% \usepackage{minipage}

\nonstopmode \title{Comparison of Variational Bayes and Minimum Description
Length Algorithms for Determining $k$ in Undirected Networks}

\author{Brett Israelsen & Joshua Rahm}


\begin{document}
\maketitle

\begin{abstract}
We have compared two different algorithms for discovering
the number of groups, $k$, in a network given no prior information about the
structure of the network. The two algorithms we have tested in this project are
the Minimum Description Length (MDL) and Variational Bayes (VB).
\end{abstract}

\section*{Introduction}

Sometimes, when given a network, it is useful to find community structure in a
network in order to be able to do further analysis into the structure of the
network. Many times, little to no prior information is given about the state of
the network is known. Given this as the case, standard modularity measures like
greedy agglomeration and the KL heuristic are more difficult to use because of their
sensitivity to degree such as in the famous Karate Club network.

To combat this, there are several algorithms used to estimate the number of groups ($k$)
in a network, an from there, a reduction algorithm may be used to determine the association
of each vertex in each of the $k$ groups.

In this paper, we have compared the results obtained from two such algorithms;
Variational Bayes and Minimum Description Length.

\section*{Background}


\section*{Approach}

\section*{Results \& Discussion}



% For tree graphs:
%
% n_i over N for each group i as a histogram
% Distribution of level by community
% 
% For Ring Graphs:
%
%   n_i over n_c
%   m_i over (choose n_c 2)
%   average degree for MDL
%
% Price:
%   
% Poisson:
%   Average degree of each group
\subsection*{\underline{Well-Known Graphs}}

\newcommand{\inputsamepage}[1] {
    \begin{minipage}{\linewidth}
        \input{#1}
    \end{minipage}
}

We have run these algorithms on graphs which are well known. And have analyzed the
results.

\subsection*{Adjective-Nouns}
\inputsamepage{include/adjnoun.tex}

\subsection*{Bow-tie}
\inputsamepage{include/bowtie.tex}

\subsection*{Dolphins}
\inputsamepage{include/dolphins.tex}

\subsection*{Les Mis\'{e}rables}
\inputsamepage{include/lesmis.tex}

\subsection*{Football}
\inputsamepage{include/football.tex}

\subsection*{Zachary Karate Club}
\inputsamepage{include/karate.tex}

\subsection*{Political Books}
\inputsamepage{include/polbooks.tex}

\subsection*{Serengeti Foodweb}
\inputsamepage{include/serengeti-foodweb.tex}

\break
\section*{Binary Trees}
\input{include/trees.tex}

\break
\section*{Ring Graphs}
\input{include/rings.tex}

\subsection*{Poisson Distrubted Random Graph}

\subsection*{Configuration Model of Existing Graphs}

\subsubsection*{Karate Club}

\subsubsection*{Sarengeti Food Web}

\subsubsection*{Political Books}

\end{document}
